Refinement of Thermostated Molecular Dynamics via Backward Error Analysis

### 2018-06-14 rigid_bodies.tex
Change of style from ACHEMSO to REVTEX

\documentclass[
journal=jctcce,
layout=twocolumn
]{achemso}

\setkeys{acs}{
	abbreviations = false,
	articletitle  = false,
	keywords      = false,
	maxauthors    = 10,
	super         = true
}

% Comment below before submitting
\let\titlefont\undefined
\usepackage[fontsize=11pt]{scrextend}
\usepackage[hidelinks,colorlinks,citecolor=blue]{hyperref}
%\flushbottom
% Comment above before submitting

\usepackage{xr}
\externaldocument{rigid_bodies_supp_info}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage[table]{xcolor}
\definecolor{lightgray}{gray}{0.9}
\usepackage{tikz}
\usetikzlibrary{decorations.text}

\newcommand{\mt}[1]{\boldsymbol{\mathbf{#1}}}   % matrix symbol
\newcommand{\vt}[1]{\boldsymbol{\mathbf{#1}}}   % vector symbol
\newcommand{\tr}[1]{#1^\text{t}}                % transposition
\newcommand{\diff}[2]{\frac{\partial #1}{\partial #2}} % derivative
\newcommand{\sdiff}[2]{\nabla^2_{#2}#1}         % 2nd derivative
\newcommand{\Ham}[1]{{\mathcal H}_\text{#1}}    % Hamiltonian
\newcommand{\Liu}[1]{i\!L_\text{#1}}            % Liouville
\newcommand{\timestep}{h}
\newcommand{\refined}[1]{\widetilde{#1}}
\newcommand{\mini}[1]{\text{\tiny{#1}}}

\usepackage{array}
\newcolumntype{L}{>{$}l<{$}}
\newcolumntype{C}{>{$}c<{$}}
\newcolumntype{R}{>{$}r<{$}}
\usepackage{booktabs}    
\usepackage[exponent-product=\times]{siunitx}

\newenvironment{smallarray}[1]                          % small arrays
{\null\,\vcenter\bgroup\scriptsize
	\renewcommand{\arraystretch}{1.5}
	\arraycolsep=.13885em
	\hbox\bgroup$\left[\array{@{}#1@{}}}
{\endarray\right]$\egroup\egroup\,\null}
\listfiles

@@

@@

\begin{acknowledgement}
	The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).
\end{acknowledgement}

\appendix
\numberwithin{equation}{section}

>>>>

\documentclass[
	aip,
	jcp,
%	preprint,
	reprint,
]{revtex4-1}

\usepackage[hidelinks,colorlinks,citecolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{natmove}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{decorations.text}

%\usepackage{xr}
%\usepackage{booktabs}
%\usepackage{threeparttable}
%\usepackage[T1]{fontenc}
%\usepackage[table]{xcolor}
%\definecolor{lightgray}{gray}{0.9}
%\usepackage[exponent-product=\times]{siunitx}

\newcommand{\mt}[1]{\boldsymbol{\mathbf{#1}}}          % matrix symbol
\newcommand{\vt}[1]{\boldsymbol{\mathbf{#1}}}          % vector symbol
\newcommand{\tr}[1]{#1^\text{t}}                       % transposition
\newcommand{\diff}[2]{\frac{\partial #1}{\partial #2}} % derivative
\newcommand{\Ham}[1]{{\mathcal H}_\text{#1}}           % Hamiltonian
\newcommand{\Liu}[1]{i\!L_\text{#1}}                   % Liouville
\newcommand{\timestep}{h}
\newcommand{\refined}[1]{\widetilde{#1}}
\newcommand{\mini}[1]{\text{\tiny{#1}}}

\newenvironment{smallarray}[1]                          % small arrays
{
	\null\,\vcenter\bgroup\scriptsize
	\renewcommand{\arraystretch}{1.5}
	\arraycolsep=.13885em
	\hbox\bgroup$\left[\array{@{}#1@{}}}
	{\endarray\right]$\egroup\egroup\,\null
}

@@

\maketitle

@@

\begin{acknowledgements}
	The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).
\end{acknowledgements}

\appendix
%\numberwithin{equation}{section}
